---
output:
  md_document:
    variant: markdown_github
---


```{r}

library(tidyverse)
list.files('code/', full.names = T, recursive = T) %>% .[grepl('.R', .)] %>% as.list() %>% walk(~source(.))
```


```{r, include=FALSE}

# Create Texevier templates for questions 1 to 4 

Texevier::create_template(directory = "/Users/riazpaleker/Documents/Mcom Economics/Data Science/R/22854843_Exam/22854843_Exam", template_name = "Question1")

Texevier::create_template(directory = "/Users/riazpaleker/Documents/Mcom Economics/Data Science/R/22854843_Exam/22854843_Exam", template_name = "Question2")

Texevier::create_template(directory = "/Users/riazpaleker/Documents/Mcom Economics/Data Science/R/22854843_Exam/22854843_Exam", template_name = "Question3")

Texevier::create_template(directory = "/Users/riazpaleker/Documents/Mcom Economics/Data Science/R/22854843_Exam/22854843_Exam", template_name = "Question4")

```




# Question One

### Source
```{r, include=FALSE}

source("code/name_persistence.R")
source("code/Names_Artists.R")
source("code/change_billboard.R")
```


### Data
```{r,include=FALSE}
Baby_Names <- readRDS("./data/US_Baby_names/Baby_Names_By_US_State.rds")
charts <- readRDS("./data/US_Baby_names/charts.rds")
HBO_Titles <- readRDS("./data/US_Baby_names/HBO_titles.rds")
HBO_Credits <- readRDS("./data/US_Baby_names/HBO_credits.rds")
```


### Packages
```{r,include=FALSE}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(stringdist)
library(gridExtra)
```

### Plot One

I can describe this plot as the name persistence (correlation) of the top 25 baby names that is lagged forward for 1,2 and 3 years. The plot itself shows the persistence in the top 25 baby names. Average correlation on the y-axis and decade on the x-axis. It is split between Male and Female Names. I began by loading the relevent packages into the function. This function has three inputs: Baby_Names, top_n_count = 25, lag = 1:3. Baby_names is our dataset and the 2nd input shows that we are looking at the top 25 baby names. The first step is to extract the top 25 baby names using piping. We then calculated the serial correlation as I believed this would show persistence in names better. We collected our correlation results. A for loop was used to repeat the same process but accounting for the 3 lags. This was embedded in a function called 'caluclate_serial_correlation' that had 3 inputs:Baby_Names, start_year, gender, lag. start_year is the year that you would want to begin with. This input is embedded in a for loop that yields the most popular names in the current year and the subsequent years. We then find the correlation which is the ratio of the common names to the top 25 names. We then find the correlation of all the names that are uniqe for a given year and gender. In our plot we do not want every year, we reduced it to decades. We can then use the ggplot function with a geomline function to plot our results (below)

```{r, echo=FALSE}
corr_plot <- name_persistence(Baby_Names, top_n_count = 25, lag = 1:3)
corr_plot
```

### Plot Two

In this plot below we matched popular names to famous artists. The names on the x-axis represents the most popular names that matched with music artists. The y-axis represents teh years. The size of the bubble represents the popularity of the name in a given year. The bigger the bubble the more popular the name. Our main function process_baby_names_and_charts has two inputs, which are our datasets. We wrangle them inside the function. We created a function inside the main one to subset baby names from 2010 to 2014 and only in New York (NY). We then craeted a function to subset the charts from 2010 to 2014. We used functions such as mutate,filter and select. We created then another function to match the names from subset_names to the artist names. We had to use the subset of names and filter it to names that needed to be plot and grouping it by Name and by Year. We used the summarise function to tally the counts. We could then plot our data using ggplot and geom_point functions.
```{r,echo=FALSE}
charts_plot <- process_baby_names_and_charts_new(Baby_Names,charts)
charts_plot
```


### Plot Three

This plot is exactly the same as the previous one. However, we just subset the charts from 2010 to 2014. We matched the data using tidyverse techniques and found the final data to plot using the same functions and techniques.

```{r, echo=FALSE}
charts_names_plot <- process_baby_names_and_charts(Baby_Names,charts)
charts_names_plot
```

# Question 2

### Source

```{r, include=FALSE}
source("code/metallic_album_popular.R")
source("code/coldplay_album_popular.R")
source("code/album_summary_table.R")
source("code/regress_metallica.R")
source("code/regress_coldplay.R")
```

### Data

```{r,include=FALSE}
coldplay <- read.csv("./Data/Coldplay_vs_Metallica/Coldplay.csv")
metallica <- read.csv("./Data/Coldplay_vs_Metallica/metallica.csv")
spoitfy <- readRDS("./Data/Coldplay_vs_Metallica/Broader_Spotify_Info.rds") 
billboard_100 <- readRDS("./Data/Coldplay_vs_Metallica/charts.rds")
```


### Plot One

In this plot we created a function to get a bar graph for most popolar (on average) Metallica Album. Our main function had one input which was our metallica dataset. We subset Metallica using filetr and !grepl() to remove rows that conisted of various names. It was not successful in all cases. we then grouped metallica by album and summarised to get the average popularity mean. We then plot the popularity of albums using ggplot and geom_bar. We flipped the co-ordinates for better visual

```{r,echo=FALSE,fig.height=6, fig.width=8, warning=FALSE}
popular_metallic_plot =popular_album_metallica(metallica)
popular_metallic_plot
```

### Plot Two

This data wrangling process is exactly the same as the first plot. We did not have to use the grepl function as the coldplay dataset did not have many different versions of the same album. we grouped by album name and got the average popularity. This was ready to plot using ggplot.

```{r,echo=FALSE,fig.height=6, fig.width=8}
popular_coldplay_plot= popular_album_coldplay(coldplay)
popular_coldplay_plot
```


### Table One

The table below compared the metrics of the top two popular albums for each band. we use filter to get the specific albums from each data set and we used the summaries function to calculate the average of each variable. we used bind_rows to bind the two filtered datasets. We used the gt function to visualise our metrics

```{r, echo=FALSE,warning=FALSE, message=FALSE}
table_album_summary = album_summary(metallica,coldplay)
table_album_summary
```


### Plot Three

We used the group_by function to group the dataset by album. We the used an lm model to regress popularity on multiple independent variables. we used ggplot, geom_point and geom_smooth to represent a scatter plot with a trend line. we did this seperately for 5 independent variables. We can view the relationship between the variables 

```{r, echo=FALSE,warning=FALSE, message=FALSE}
combined_reg_plot <- regress_metallica(metallica)
combined_reg_plot
```


### Plot Four

Plot four is the same regression analysis and plot but for Coldplay. The data wrangling and plotting was conducted in the same way as the previous plot.

```{r, echo=FALSE,warning=FALSE, message=FALSE}
combined_reg_plot_coldplay <- regress_coldplay(coldplay)
combined_reg_plot_coldplay

```


# Question Three


### Source

```{r,include=FALSE}
source("code/Aid_alloc_plot.R")
source("code/Aid_Commit_plot.R")
source("code/combine_plot.R")

```


### Data

```{r,include=FALSE}
alloc <- read.csv("./data/Ukraine_Aid/Financial Allocations.csv")
commit <- read.csv("./Data/Ukraine_Aid/Financial Commitments.csv")
```


### Plot One

This graph shows the allocation of EU countries for humanitarian aid. We created a function which had one input (Alloc dataset). we used the piping function to subset our data. We used filter to get EU members only, then used select to remove EU members as a variables in the next line we used gather to make our data set long. We the subset our data further to contain only humanitarian aid. We then used ggplot with geom_bar to plot.

```{r, echo=FALSE}
Humanatarian_Aid_alloc_plot = Aid_alloc(alloc)
Humanatarian_Aid_alloc_plot
```

### Plot Two

This data wrangling process followed the exact steps as above. We just used the commit data set. The graph shows the EU countries that made a commitment to provide humanitarian aid. We created a function which had one input (Commit dataset). we used the piping function to subset our data. We used filter to get EU members only, then used select to remove EU members as a variables in the next line we used gather to make our data set long. We the subset our data further to contain only humanitarian aid. We then used ggplot with geom_bar to plot.

```{r, echo=FALSE}
Humanatarian_Aid_Commit_plot = Aid_commit(commit)
Humanatarian_Aid_Commit_plot
```

### Plot Three

The graphs below show the EU countries with two bars for each countries. The red bar indicating allocationa and blue representing commitment. This is for humanatraian aid. We first had to wrangle the alloc data. We did the exact same thing for the first plotWe created a function which had one input (Commit dataset). we used the piping function to subset our data. We used filter to get EU members only, then used select to remove EU members as a variables in the next line we used gather to make our data set long. We the subset our data further to contain only humanitarian aid. The same was done for commit. This was all under the combine_plots function. We combined our data from a wide format and then turned it long using gather for a representing purpose. We used a ggplot and geom_bar to plot the data.


```{r, echo=FALSE, warning=FALSE}
combined_plots = combine_plots(alloc,commit)
combined_plots
```

# Question Four

### Source
```{r,include=FALSE}
source("code/GDP_plot.R")
source("code/GDPvMedal.R")
source("code/Dominance_plot.R")
source("code/overperform_summer.R")
source("code/overperform_winter.R")
```

### Data
```{r, include=FALSE}
winter <- readRDS("./Data/olympics/winter.rds") 
summer <- readRDS("./Data/olympics/summer.rds") 
GDP <- readRDS("./Data/olympics/GDP.rds")
```

### Plot One

This graph shows the gold, silver and bronze tally for specific countries: emerging markets, south american countries and countries with a similar economy size to India. Our two inputs is the summer and GDP data sets which are wrangled. We subset GDP to get the GDP per capita variable in descending order. We then extracted certain countries that we wanted to compare to India. We wrangled our summer data set using the piping and the filter function to match the countries to the countries that we have chosen to compare. We then calculated medals per country and using summarise to count sports teams as only one medal. we used distinct to find the distinct Year, Country, Sport and Medal. we grouped our data by country and medal before we used the summary function. We wanted to have 3 barplots per country we need a wide format data to have colomns for each type of medal. We then turned it back into the long format such that we can use ggplot and geom_bar functions.


```{r, echo=FALSE, fig.width=8}
GDP_plot =GDP_per_capita(GDP,summer)
GDP_plot
```

### Plot Two

The plot below has GDP per Capita on the x-axis and Medal count on the y-axis. The countries are the points in the graph in its respective position. This shows a country's medal count given its per capita GDP. Our function has two inputs which are our summer and GDP datasets. We subset our GDP data to only include country name and gdp per capita. we remove certain colomns. We have a data frame of country codes. We filtered our gdp data to keep only countries with that code. We used filter on the summer data to keep the certain countries and used left_join to make one dataset. We used a different way in this plot to get the medal count. We identified that number of payers in large team sports for diffrent sports. we used a ifelse function to tally only one medal if the respective team sport was matched. we then grouped our subset of summer data to group by country and gdp per capita and summary to sum the adjusted medal counts. We used ggplot for the axis and geom_point to plot the countries.

```{r,echo=FALSE, fig.width=8}
point_olympic_plot <- GDP_per_capita_medal(GDP,summer)
point_olympic_plot
```


### Plot Three

```{r,echo=FALSE, fig.width=8, warning=FALSE, message=FALSE}
combined_dominance_plot <- dominance_plot(summer,winter)
grid::grid.draw(combined_dominance_plot)
```
