---
title: "European Union (EU) Aid in Russia-Ukraine Conflict"
documentclass: elsarticle
Thesis_FP: false
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: true
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Jane Doe^
Ref1: Some Institution, Cape Town, South Africa
Email1: nfkatzke\@gmail.com
Author2: John Smith
Ref2: Some other Institution, Cape Town, South Africa
Email2: John\@gmail.com
CommonAffiliation_12: true
Author3: John Doe
Email3: Joe\@gmail.com
CorrespAuthor_1: true
keywords: Multivariate GARCH \sep Kalman Filter \sep Copula
JELCodes: L250 \sep L100
BottomRFooter: \footnotesize Page \thepage
addtoprule: true
addfootrule: true
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: true
linenumbers: false
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: true
Journal: Journal of Finance
toc: false
numbersections: true
fontsize: 11pt
linestretch: 1.2
link-citations: true
AddTitle: true
abstract: An analysis on the commitment and allocation of humanitarian aid from EU countries
---


```{r setup, include=FALSE}

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

alloc <- read.csv("./data/Ukraine_Aid/Financial Allocations.csv")
commit <- read.csv("./Data/Ukraine_Aid/Financial Commitments.csv")
```

```{r, include=FALSE}
# all my functions to be called
source("code/Aid_alloc_plot.R")
source("code/Aid_Commit_plot.R")
source("code/combine_plot.R")
```


# Allocations

* The figure below represents the humanitarian allocations from EU countries. We find that Estonia and France are the only countries that significantly allocated humanitarian aid to its budget
* Italy, Sweeden and Bulguria have also allocated some budget for aid
* Germany, Croatia, Netherlands, Poland, Slovakia have all allocated almost no aid to its budget

```{r, echo=FALSE}
Humanatarian_Aid_alloc_plot = Aid_alloc(alloc)
Humanatarian_Aid_alloc_plot
```

# Commitment

* This figure shows the commitment (promise) that EU countries have to allocate humunaitarian aid.
* Germany, Netherlands and Poland are notable countries who have committed in providing the most aid

```{r, echo=FALSE}
Humanatarian_Aid_Commit_plot = Aid_commit(commit)
Humanatarian_Aid_Commit_plot
```

# Allocation vs Commitment

* This figure shows a side-by-side graph of the commitment (blue) versus allocation (red) of humanitarian aid by the EU countries
* There are a few countries such as Sweden, Spain and Belgium that has allocated just as much as they have committed
* Germany is an interesting case as they have committed a significant amount of aid but has so far allocated none to its budget. Netherlands and Poland are in a similar position
* Countries such as France, Estonia and Italy have done the complete opposite. They have allocated more funds than what they promised to commit.
* This is a refreshing sign from these few countries that have placed a high importance on humanitarian aid.
```{r, echo=FALSE, warning=FALSE}
combined_plots = combine_plots(alloc,commit)
combined_plots
```

# Other Talking Points

* A figure was not constructed but we can also compare how much spending is dedicated towards the country's military.
* We can compare if this exceeds the allocated humanitarian aid.
* This will also help us understand the commitment or weight of importance that EU countries place on the conflict

